The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Discursion

\section{Discussion} \label{discussion}
In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.

\subsection{RQ1 Answer}  
RQ1: What drives API evolution?

@@

1.

       %Answer to RQ
       Functionality is the main driver for change, and it catalyses other changes

       %Point to results
       relate to enhancive types
       relate to functionality related laws

       %Relate to literature
       Refute refactorings paper
       Maybe something else

2. 
       %Answer to RQ
       Talk about the results regarding the law of familiarity that didn't apply.

       %Point to results

       %Relate to literature
       Cite the papers that say u shoulnt change APIs and say that our results agree \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers} 
       Explain our results with this: 
              1. The laws are not immutable, since they arise from the habits and practices of humans. [1980programs]
              2. If laws governing large-program evolution can be formulated at all, they must certainly be weaker than those formulated in the biological sciences, where regularity stems from the collective behavior of cellular systems that, even though alive, are nonintelligent, i.e., are not influenced by conscious thought processes, at least at the level of human understanding. [On Understanding Laws, Evolution, and Conservation in the Large-Program Life Cycle]

@@

---------------------------------------------

@@

%       -How will our study help other companies? (Less important)

%Discuss and evaluate conflicting explanations of the results. This is the sign of a good discussion.

>>>>

\newpage
\section{Discussion} \label{discussion}
In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.

\newpage
\subsection{RQ1 Answer}

@@

In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs go through (!!!FIND PAPERS TO CITE HERE). These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change and that they rather are ripple-effects of changes to functionality.

Our results found that seven out of eight of Lehman's laws do apply to API evolution. The law of Conservation of Organisational Stability was found not to apply, since changes to APIs are often discouraged (!!!reword) by the fear that it will disrupt the applications using the API. This inertia to change in API evolution is supported by other research, which also conclude that the negative effect that changes to APIs may have is a major factor to be considered \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.

Based on our results, we form the conclusion that the hunger (reword) for functionality and the fear (reword) of changing are two opposing forces that cause updates to APIs to be infrequent. In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!reword). This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}. The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.

@@

@@

--------------------------------------------------------------------------
